Reproduce anaylses of Beninca et al (2008)

### 2016-02-12 code/report.Rmd
update report

qplot(x=as.vector(original.cors), y=as.vector(cor.coefs), ylim = c(-0.4,0.4), xlim=c(-0.4, 0.4),
      xlab="Correlations in original article", ylab="Correlations calculated in this reproduction") + geom_abline(intercept=0,slope=1, colour="red")
```

@@

Compare graphically with original LEs
```{r}
## read in LE values given in original publication
original.LEs <- read.csv(text=getURL(paste0(repo,"/data/original_direct_LEs.csv")), skip=0, header=T)
both_LEs <- full_join(original.LEs, LEs) # merge the reproduced and original values
ggplot(both_LEs, aes(x=LE, y=le)) + geom_point() + xlim(0.02, 0.09) + ylim(0.02, 0.09) + geom_abline(intercept=0, slope=1) +
  xlab("Lyapunov exponent from original article") + ylab("Reproduced Lyapunov exponent")
```

@@

## and plot time series
g1 <- ggplot(mt, aes(x=as.numeric(Day.number), y=sqrt(value))) +
  facet_wrap(~variable, ncol=2, scales="free_y") +
  geom_line(size=0.5, col="black") +
  scale_colour_manual(values = species.colour.mapping)
g2 <- geom_line(data=from.steve, aes(x=Day.number, y=sqrt(value_steve)), col="red")
g1 + g2

## same but to allow x-y scatter
mt$Day.number <- as.character(mt$Day.number)
from.steve$Day.number <- as.character(from.steve$Day.number)
ff <- inner_join(mt, from.steve)
mt$Day.number <- as.numeric(mt$Day.number)
from.steve$Day.number <- as.numeric(from.steve$Day.number)
ff$Day.number <- as.numeric(ff$Day.number)
#str(ff)
#ff$difference <- ff$value - ff$value_steve
#qplot(log10(ff$difference))
qplot(data=ff, x=log10(value_steve), y=log10(value)) +
  xlab("Values from Ellner (log 10 transformed)") +
  ylab("Reproduced values (log 10 transformed)") +
  geom_abline(intercept=0, slope=1, colour="red")

>>>>

qplot(x=as.vector(original.cors), y=as.vector(cor.coefs), ylim = c(-0.4,0.4), xlim=c(-0.4, 0.4),
      xlab="Correlations in original article", ylab="Correlations calculated\nin this reproduction") + geom_abline(intercept=0,slope=1, colour="red")
```

@@

Compare graphically with original LEs
```{r}
## read in LE values given in original publication
original.LEs <- read.csv(text=getURL(paste0(repo,"/data/original_direct_LEs.csv")), skip=0, header=T)
both_LEs <- full_join(original.LEs, LEs) # merge the reproduced and original values
ggplot(both_LEs, aes(x=LE, y=le)) +
  geom_point() +
  xlim(0.02, 0.09) +
  ylim(0.02, 0.09) +
  geom_abline(intercept=0, slope=1, colour="red") +
  xlab("Lyapunov exponent from original article") + 
  ylab("Reproduced Lyapunov exponent")
```

@@

## and plot time series
g1 <- ggplot(mt, aes(x=as.numeric(Day.number), y=sqrt(value))) +
  facet_wrap(~variable, ncol=2, scales="free_y") +
  geom_line(size=0.5, col="black") +
  scale_colour_manual(values = species.colour.mapping)
g2 <- geom_line(data=from.steve, aes(x=Day.number, y=sqrt(value_steve)), colour="red")
g1 + g2

## same but to allow x-y scatter
mt$Day.number <- as.character(mt$Day.number)
from.steve$Day.number <- as.character(from.steve$Day.number)
ff <- inner_join(mt, from.steve)
mt$Day.number <- as.numeric(mt$Day.number)
from.steve$Day.number <- as.numeric(from.steve$Day.number)
ff$Day.number <- as.numeric(ff$Day.number)
#str(ff)
#ff$difference <- ff$value - ff$value_steve
#qplot(log10(ff$difference))
qplot(data=ff, x=log10(value_steve), y=log10(value)) +
  xlab("Values from Ellner\n(log 10 transformed)") +
  ylab("Reproduced values\n(log 10 transformed)") +
  geom_abline(intercept=0, slope=1, colour="red")
